--- 
title: "Ryten lab induction book"
author: 
    - David Zhang^[UCL, david.zhang.12@ucl.ac.uk]
    - Regina Reynolds^[UCL, regina.reynolds.16@ucl.ac.uk]
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rytenlab/ryten_induction
description: "Induction bookdown for all things Ryten lab"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> The goal of this book is to provide instructions to that you'll need to get started in the Ryten lab as well as 

# Welcome!

We hope you enjoy your time in the Ryten lab! Some description about the book... **TO BE ADDED**

## Acknowledgements

For example, this book was made possible thanks to the R package `bookdown` [@R-bookdown].

The below code automatically generates the `packages.bib`, a `bibtex` format for all the packages listed. If you contribute to this book and include a particular R package in your guide (as with `bookdown` above), consider adding it to the code chunk and citing it via including `[@R-package_name]` in the text.

```{r r_package_references, include = TRUE}
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
