--- 
title: "Ryten lab induction book"
author: 
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rytenlab/ryten_induction
description: "Induction bookdown for all things Ryten lab"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> The goal of this book is to provide a guide for your Ryten lab journey

# Welcome!

We hope you enjoy your time in the Ryten lab! The goal of this book is to capture the tasks we share as a team and document the things we would have liked to have known when beginning in the Ryten lab. 

# Useful links

- The Ryten lab [website](https://rytenlab.com/)
- The Ryten lab [GitHub](https://github.com/rytenlab)
- The Ryten lab [Sharepoint](https://liveuclac.sharepoint.com/sites/rytenlab/Shared Documents/). To access this, you must be a member of rytenlab (if you are receiving e-mails from rytenlab@live.ucl.ac.uk, then you are a member). If you are a not a member, let one of the existing members know and we'll add you.

## Acknowledgements

This book was made possible thanks to the R package `bookdown` [@R-bookdown].

The below code automatically generates `packages.bib`, a `bibtex` format for all the packages listed. If you contribute to this book and include a particular R package in your guide (as with `bookdown` above), consider adding it to the code chunk and citing it via including `[@R-package_name]` in the text.

```{r r_package_references, include = TRUE}
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
